---
title: Hands-on exercise 1
--- 


1. Create a new `Quarto` doc and specifiy in yaml header the following:

```{yaml}
format:
    pdf: 
        documentclass: ___
        number-sections: true 
```

Where you can explore different options. Create a KOMA report `scr..` 

2. Add the following sections and cross-reference each one with `{#sec-___}`

```{markdown}
# Overview 

# Introduction 

## background 

## Objectives 

# Methods 
```

3. Add to yaml header table of contents `toc`, list of figures `lof` and list of tables, `lot` 

4. Change the name for (3) to **Index**, **Figures in-text**, and **Tables in-text**. hint: `crossref` options in yaml header. 
   
5. Add the following chuncks within your report body and reference them
Global: 

```{r}
#| echo: fenced 
#| warning: false 
library(tidyverse)
library(gt)
```

Figure: 

```{r}
#| echo: fenced
#| output: false
#| fig-cap: __________
#| label: fig-____

ggplot(Theoph, aes(Time, conc)) + 
geom_point() + 
theme_bw(base_size = 13)
```

Table: 


```{r}
#| echo: fenced 
#| output: false 
#| label: tbl-___
#| tbl-cap: ______

Theoph |>
filter(Subject == 1, row_number() <= 5) |>
gt() 
```


6. Bibliography: using RStudio Visual Editor, cite a paper or R package using the synatx for citations and print references prior to `Methods` section 


7. Bonus: Change font using the following code

```{yaml}
mainfont: LiberationSerif
sansfont: LiberationSans
monofont: LiberationMono
```
